---
title: "Hidden invalidity among fifteen commonly used measures in social and personality psychology"
author: "Ian Hussey^[Ghent University. Email: ian.hussey@ugent.be]"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

# To do

- when this is solid, make sure stats are produced for all the remaining scales. some are now missing. this also fucks with the alluvial plot.
- NFCC_A_subscale is all NA. check original data processing. nb "#pearson_r_estimate(data = dependability_data, Scale = "NFCC_A")," and "#pearson_r_estimate(data = stability_data, Scale = "NFCC_A")," are commented out
- combine tables and below needs work, as ive broken sth. N and MI seem to be broken.
- re boot the internal consistencies
- measurement_invariance_full_results writes appreviated scale names to disk. fix?
- based on this, check that the summary table counts are right (ie no double counting)
- should plots, tables etc split by full/split scales or not? does the full table mention this distinction?

# Decision making criteria

CFA

- Note somewhere that item reverse scoring has already been done; we are not interested in method factors such as reverse wordings, only interpretative factors.
- Fit indices
- Chi^2 assesses absolute fit. It is sample size dependant, and given our sample sizes will be significant in almost all cases and is therefore not informative. However, it is still important to report along with its degrees of freedom and associated p value (Kline, 2005; Hayduk et al, 2007). 
- Standardized Root Mean Residual (SRMR) assesses absolute fit too. 
- Tuckler-Lewis Fit Index (TLI) assesses Relative Fit. Compares to a null model, although is not a hypothesis test. Sample size independent, which is important here.
- Root Mean Square Error of Approximation (RMSEA) assesses Noncentrality.
- Bentler’s Comparative Fit Index (CLI) assesses Noncentrality.

- Hu and Bentler (1999) suggest a two-index presentation format of either SRMR with the CFI, TLI, or RMSEA. We'll report all four metrics and make a composite of all three two-index scores:
  - CLI >= .95 & SRMR <= .09
  - TFI >= .95 & SRMR <= .09
  - RMSEA <= .06 & SRMR <= .09
  - "We reccomend that practitioners use a cutoff value close to .95 for TLI (CFI) in combination with a cutoff value close to .09 for SRMR to evaluate model fit...A combination rule with RMSEA > .06 and SRMR > .09 (or .10) resulted in the least sum of Type I and II error rates (pps 27-28)."

MI tests

- MI via model fit indices (Chen, 2007; Putnick & Bornstein, 2016; see also Cheung & Rensvold, 2002; Meade et al., 2008).
- Configural invariance failure: same as CFA above.
- Metric and scalar invariance failure: delta_RMSEA > 0.01 or delta_CFI < -0.015

Overall scale evaluations

- For a scale to be rated "good" it must demonstrate good internally consistency, stable across time (both immediately and over time), it must conform to the expected factor structure, and it must be invariant across age and gender.
- Criterion: omega_t >= .7 & dependability >= .7 & stability >= .7 & CFA fit >= Mixed & MI passed for both median age and gender

```{r, include=FALSE}
knitr::opts_chunk$set(message=FALSE,
                      warning=FALSE,
                      cache=TRUE,
                      cache.lazy=TRUE)
```

```{r}

# dependencies
library(tidyverse)
library(lavaan)
library(semTools)
library(knitr)
library(kableExtra)
library(timesavers)  # library(devtools); install_github("ianhussey/timesavers")
library(moments)
library(plotrix)
library(lubridate)
library(psych)
library(rsample)
library(purrr)
library(ggalluvial)
library(patchwork)

# options
options(knitr.table.format = "html") # necessary configuration of tables

# disable scientific notation
options(scipen = 999) 

# set seed for reproducability
set.seed(42)

# print versions of packages used, R version, OS details.
writeLines(capture.output(sessionInfo()), "session_info.txt")

```

# Data

## Get data

```{r}

# get data
load("../data/trimmed_data.RData")

# trim to include only the first timepoint per user_id per scale
# ie exclude repeat participations on the same scale
trimmed_first_timepoint_per_user_per_scale <- trimmed_data %>%
  arrange(user_id, individual_differences_measure, datetime_ymdhms) %>%
  mutate(combined_var = paste0(user_id, individual_differences_measure)) %>%
  filter(combined_var != lag(combined_var)) %>%
  dplyr::select(-combined_var)

# manually compiled data on k items, k factors, and changes made to scales compared to original publications.
additional_scale_data <- read.csv("../data/additional_scale_data.csv")


count(trimmed_data, NFCC_A_subscale)

```

## Subset data

```{r}


# find median age to split by.
# Because individuals can participate more than once, and their age is recorded as age at participation, repeat participations
# overrepresent that participant's age when finding medians. Given we can't assume that repeate participations are evenly distributed across ages, # we must instead construct a median age for the whole sample. 
# This also ensures that the same median age is used for all scales.

median_age <- trimmed_first_timepoint_per_user_per_scale %>%
  group_by(user_id) %>%
  summarize(mean_age_by_participant = mean(age)) %>%  # given repeat presentations with changing age
  ungroup() %>%
  summarize(median_age = median(mean_age_by_participant)) %>%
  pull(median_age) %>%
  round(0)

# split scales

bfi_e_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(bfi_e1, bfi_e2, bfi_e3, bfi_e4, bfi_e5, bfi_e6, bfi_e7, bfi_e8, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

bfi_c_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(bfi_c1, bfi_c2, bfi_c3, bfi_c4, bfi_c5, bfi_c6, bfi_c7, bfi_c8, bfi_c9, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

bfi_n_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(bfi_n1, bfi_n2, bfi_n3, bfi_n4, bfi_n5, bfi_n6, bfi_n7, bfi_n8, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

bfi_a_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(bfi_a1, bfi_a2, bfi_a3, bfi_a4, bfi_a5, bfi_a6, bfi_a7, bfi_a8, bfi_a9, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

bfi_o_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(bfi_o1, bfi_o2, bfi_o3, bfi_o4, bfi_o5, bfi_o6, bfi_o7, bfi_o8, bfi_o9, bfi_o10, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

bidr_im_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(bidr_im1, bidr_im2, bidr_im3, bidr_im4, bidr_im5, bidr_im6, bidr_im7, bidr_im8, 
                bidr_im9, bidr_im10, bidr_im11, bidr_im12, bidr_im13, bidr_im14, bidr_im15, 
                bidr_im16, bidr_im17, bidr_im18, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

bidr_sde_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(bidr_sde1, bidr_sde2, bidr_sde3, bidr_sde4, bidr_sde5, bidr_sde6, bidr_sde7, bidr_sde8, 
                bidr_sde9, bidr_sde10, bidr_sde11, bidr_sde12, bidr_sde13, bidr_sde14, bidr_sde15, bidr_sde16, 
                bidr_sde17, bidr_sde18, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

bjw_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(bjw1, bjw2, bjw3, bjw4, bjw5, bjw6, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

brs_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(brs1, brs2, brs3, brs4, brs5, brs6, brs7, brs8, brs9, brs10, brs11, brs12, brs13, brs14, brs15, brs16, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

he_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(he1, he2, he3, he4, he5, he6, he7, he8, he9, he10, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

icat_o_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(icat_o1, icat_o2, icat_o3, icat_o4, icat_o5, icat_o6, icat_o7, icat_o8, icat_o9, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

icat_s_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(icat_s1, icat_s2, icat_s3, icat_s4, icat_s5, icat_s6, icat_s7, icat_s8, icat_s9, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

nfc_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(nfc1, nfc2, nfc3, nfc4, nfc5, nfc6, nfc7, nfc8, nfc9, 
                nfc10, nfc11, nfc12, nfc13, nfc14, nfc15, nfc16, nfc17, nfc18, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

nfcc_p_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(nfcc_p1, nfcc_p2, nfcc_p3, nfcc_p4, nfcc_p5, nfcc_p6, nfcc_p7, nfcc_p8, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

nfcc_d_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(nfcc_d1, nfcc_d2, nfcc_d3, nfcc_d4, nfcc_d5, nfcc_d6, nfcc_d7, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

nfcc_c_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(nfcc_c1, nfcc_c2, nfcc_c3, nfcc_c4, nfcc_c5, nfcc_c6, nfcc_c7, nfcc_c8, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

nfcc_a_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(nfcc_a1, nfcc_a2, nfcc_a3, nfcc_a4, nfcc_a5, nfcc_a6, nfcc_a7, nfcc_a8, nfcc_a9, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

nfcc_o_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(nfcc_o1, nfcc_o2, nfcc_o3, nfcc_o4, nfcc_o5, 
                nfcc_o6, nfcc_o7, nfcc_o8, nfcc_o9, nfcc_o10, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

pe_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(pe1, pe2, pe3, pe4, pe5, pe6, pe7, pe8, pe9, pe10, pe11, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

pns_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(pns1, pns2, pns3, pns4, pns5, pns6, pns7, pns8, pns9, pns10, pns11, pns12, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

rse_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(rse1, rse2, rse3, rse4, rse5, rse6, rse7, rse8, rse9, rse10, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

rwa_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(rwa1, rwa2, rwa3, rwa4, rwa5, rwa6, rwa7, rwa8, rwa9, rwa10, 
                rwa11, rwa12, rwa13, rwa14, rwa15, rwa16, rwa17, rwa18, rwa19, rwa20, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

sdo_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(sdo1, sdo2, sdo3, sdo4, sdo5, sdo6, sdo7, sdo8, sdo9, sdo10, sdo11, sdo12, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

sm_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(sm1, sm2, sm3, sm4, sm5, sm6, sm7, sm8, sm9, 
                sm10, sm11, sm12, sm13, sm14, sm15, sm16, sm17, sm18, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

soc_ic_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(soc_ic1, soc_ic2, soc_ic3, soc_ic4, soc_ic5, 
                soc_ic6, soc_ic7, soc_ic8, soc_ic9, soc_ic10, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

soc_pe_data <- trimmed_first_timepoint_per_user_per_scale %>%
  dplyr::select(soc_pe1, soc_pe2, soc_pe3, soc_pe4, soc_pe5, soc_pe6, soc_pe7, soc_pe8, soc_pe9, soc_pe10, sex, age) %>%
  na.omit() %>%
  mutate(age = ifelse(age < median_age, 0, 1))

```

### Test-retest data

```{r}

## get and reshape data

# separate out user_ids with two timepoints per scale
user_ids_with_two_timepoints_per_scale <- trimmed_data %>%
  dplyr::select(user_id, session_id, datetime_ymdhms, individual_differences_measure) %>%
  count(user_id, individual_differences_measure) %>%
  filter(n >= 2)

# semi join with full data
two_timepoints_per_scale <- trimmed_data %>%
  semi_join(user_ids_with_two_timepoints_per_scale, 
            by = c("user_id", "individual_differences_measure")) %>%
  arrange(user_id, individual_differences_measure, datetime_ymdhms) %>%
  mutate(combined_var = paste0(user_id, individual_differences_measure),
         timepoint = ifelse(combined_var == lag(combined_var, n = 2), 3, 
                            ifelse(combined_var == lag(combined_var, n = 1), 2 , 1)),
         # lag can't operate on the first row, so mung a solution to this.
         timepoint = ifelse(is.na(timepoint), 1, timepoint)) %>%
  filter(timepoint %in% c(1, 2)) %>%
  dplyr::select(user_id, datetime_ymdhms, timepoint, individual_differences_measure,
                individual_differences_sum_score)

# rehape t1
timepoint_1 <- two_timepoints_per_scale %>%
  filter(timepoint == 1) %>%
  rename(individual_differences_sum_score_t1 = individual_differences_sum_score,
         datetime_ymdhms_t1 = datetime_ymdhms) %>%
  dplyr::select(-timepoint)

# reshape t2
timepoint_2 <- two_timepoints_per_scale %>%
  filter(timepoint == 2) %>%
  rename(individual_differences_sum_score_t2 = individual_differences_sum_score,
         datetime_ymdhms_t2 = datetime_ymdhms) %>%
  dplyr::select(-timepoint)

# join
two_timepoint_scores_temp <- timepoint_1 %>%
  left_join(timepoint_2, by = c("user_id", "individual_differences_measure")) %>%
  mutate(days_to_followup = as.duration(interval(start = ymd_hms(datetime_ymdhms_t1), 
                                                 end = ymd_hms(datetime_ymdhms_t2))),
         days_to_followup = round(as.numeric(days_to_followup, "days"), 3)) %>%
  na.omit


## for the BFI and NFCC sub scales, we need the subscale sum score rather than the full scale sum score. 

### BFI

#### bfi t1
timepoint_1_bfi_temp <- two_timepoint_scores_temp %>%
  filter(individual_differences_measure %in% c("BFI-Part 1", "BFI-Part 2")) %>%
  select(user_id, datetime_ymdhms_t1, individual_differences_measure)

timepoint_1_bfi <- trimmed_data %>%
  rename(datetime_ymdhms_t1 = datetime_ymdhms) %>%
  semi_join(timepoint_1_bfi_temp, 
            by = c("user_id", "individual_differences_measure", "datetime_ymdhms_t1")) %>%
  select(user_id, datetime_ymdhms_t1, BFI_E_subscale, BFI_C_subscale, BFI_N_subscale, BFI_A_subscale, BFI_O_subscale) %>%
  rename(BFI_E = BFI_E_subscale,
         BFI_C = BFI_C_subscale,
         BFI_N = BFI_N_subscale,
         BFI_A = BFI_A_subscale,
         BFI_O = BFI_O_subscale) %>%
  gather(individual_differences_measure, individual_differences_sum_score_t1, 
         c("BFI_E", "BFI_C", "BFI_N", "BFI_A", "BFI_O")) %>%
  na.omit

#### bfi t2
timepoint_2_bfi_temp <- two_timepoint_scores_temp %>%
  filter(individual_differences_measure %in% c("BFI-Part 1", "BFI-Part 2")) %>%
  select(user_id, datetime_ymdhms_t2, individual_differences_measure)

timepoint_2_bfi <- trimmed_data %>%
  rename(datetime_ymdhms_t2 = datetime_ymdhms) %>%
  semi_join(timepoint_2_bfi_temp, 
            by = c("user_id", "individual_differences_measure", "datetime_ymdhms_t2")) %>%
  select(user_id, datetime_ymdhms_t2, BFI_E_subscale, BFI_C_subscale, BFI_N_subscale, BFI_A_subscale, BFI_O_subscale) %>%
  rename(BFI_E = BFI_E_subscale,
         BFI_C = BFI_C_subscale,
         BFI_N = BFI_N_subscale,
         BFI_A = BFI_A_subscale,
         BFI_O = BFI_O_subscale) %>%
  gather(individual_differences_measure, individual_differences_sum_score_t2, 
         c("BFI_E", "BFI_C", "BFI_N", "BFI_A", "BFI_O")) %>%
  na.omit

#### combine
two_timepoint_scores_bfi <- 
  full_join(timepoint_1_bfi, timepoint_2_bfi, by = c("user_id", "individual_differences_measure")) %>%
  mutate(days_to_followup = as.duration(interval(start = ymd_hms(datetime_ymdhms_t1), 
                                                 end = ymd_hms(datetime_ymdhms_t2))),
         days_to_followup = round(as.numeric(days_to_followup, "days"), 3))

### NFCC

#### nfcc t1
timepoint_1_nfcc_temp <- two_timepoint_scores_temp %>%
  filter(individual_differences_measure %in% c("NFCC, Part 1", "NFCC, Part 2")) %>%
  select(user_id, datetime_ymdhms_t1, individual_differences_measure)

timepoint_1_nfcc <- trimmed_data %>%
  rename(datetime_ymdhms_t1 = datetime_ymdhms) %>%
  semi_join(timepoint_1_nfcc_temp, 
            by = c("user_id", "individual_differences_measure", "datetime_ymdhms_t1")) %>%
  select(user_id, datetime_ymdhms_t1, NFCC_A_subscale, NFCC_O_subscale, NFCC_P_subscale, NFCC_D_subscale, NFCC_C_subscale) %>%
  rename(NFCC_A = NFCC_A_subscale,
         NFCC_O = NFCC_O_subscale,
         NFCC_P = NFCC_P_subscale,
         NFCC_D = NFCC_D_subscale,
         NFCC_C = NFCC_C_subscale) %>%
  gather(individual_differences_measure, individual_differences_sum_score_t1, 
         c("NFCC_A", "NFCC_O", "NFCC_P", "NFCC_D", "NFCC_C")) %>%
  na.omit


#### nfcc t2
timepoint_2_nfcc_temp <- two_timepoint_scores_temp %>%
  filter(individual_differences_measure %in% c("NFCC, Part 1", "NFCC, Part 2")) %>%
  select(user_id, datetime_ymdhms_t2, individual_differences_measure)

timepoint_2_nfcc <- trimmed_data %>%
  rename(datetime_ymdhms_t2 = datetime_ymdhms) %>%
  semi_join(timepoint_2_nfcc_temp, 
            by = c("user_id", "individual_differences_measure", "datetime_ymdhms_t2")) %>%
  select(user_id, datetime_ymdhms_t2, NFCC_A_subscale, NFCC_O_subscale, NFCC_P_subscale, NFCC_D_subscale, NFCC_C_subscale) %>%
  rename(NFCC_A = NFCC_A_subscale,
         NFCC_O = NFCC_O_subscale,
         NFCC_P = NFCC_P_subscale,
         NFCC_D = NFCC_D_subscale,
         NFCC_C = NFCC_C_subscale) %>%
  gather(individual_differences_measure, individual_differences_sum_score_t2, 
         c("NFCC_A", "NFCC_O", "NFCC_P", "NFCC_D", "NFCC_C")) %>%
  na.omit

#### combine
two_timepoint_scores_nfcc <- 
  full_join(timepoint_1_nfcc, timepoint_2_nfcc, by = c("user_id", "individual_differences_measure")) %>%
  mutate(days_to_followup = as.duration(interval(start = ymd_hms(datetime_ymdhms_t1), 
                                                 end = ymd_hms(datetime_ymdhms_t2))),
         days_to_followup = round(as.numeric(days_to_followup, "days"), 3))


## exclude the bfi and nfcc sum scores and replace with the subscale sum scores


two_timepoint_scores <- two_timepoint_scores_temp %>%
  filter(!(individual_differences_measure %in% c("BFI-Part 1", "BFI-Part 2", "NFCC, Part 1", "NFCC, Part 2"))) %>%
  rbind(two_timepoint_scores_bfi) %>%
  rbind(two_timepoint_scores_nfcc)

```

```{r}

## quick analyses of timepoint data to understand distributions

# percent with test retest data
n_with_test_retest_data <- round(nrow(two_timepoint_scores), 1)

percent_with_test_retest_data <- round(nrow(two_timepoint_scores) / nrow(trimmed_first_timepoint_per_user_per_scale)*100, 1)

# days to follow-up
two_timepoint_scores %>%
  summarise(min = min(days_to_followup),
            max = max(days_to_followup),
            sd = sd(days_to_followup),
            median = median(days_to_followup),
            mean = mean(days_to_followup)) %>%
  round_df(2) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

data.frame(quantile = quantile(two_timepoint_scores$days_to_followup)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

`r n_with_test_retest_data` user_ids (`r percent_with_test_retest_data`%) had test-retest data on the same scale available. 

Retest times are highly skewed. Most reparticipated the same day, the vast majority within a week, but some up to multiple years later. 

# Scale details

Used later on in several tests or for reporting

```{r}

joiner_data_frame <- 
  data.frame(Scale = c("BFI-E", "BFI-E", "BFI-E", "BFI-A", "BFI-A", "BIDR-IM", "BIDR-SDE", "BJW", "BRS",
                       "HE", "ICAT-O", "ICAT-S", "NFC", "NFCC-PDC", "NFCC-PDC", "NFCC-PDC", "NFCC-AO",
                       "NFCC-AO", "PE", "PNS", "RSE", "RWA", "SDO", "SM", "SOC-IC", "SOC-PE"),
             Scales_all = c("BFI-E", "BFI-C", "BFI-N", "BFI-A", "BFI-O", "BIDR-IM", "BIDR-SDE", "BJW", "BRS", "HE",
                            "ICAT-O", "ICAT-S", "NFC", "NFCC-P", "NFCC-D", "NFCC-C", "NFCC-A", "NFCC-O", "PE", "PNS",
                            "RSE", "RWA", "SDO", "SM", "SOC-IC", "SOC-PE"))

# trim data
n_per_scale <- trimmed_first_timepoint_per_user_per_scale %>%
  rename(Scale = individual_differences_measure) %>%
  count(Scale) %>%
  mutate(Scale = dplyr::recode(Scale,
                               "BFI-Part 1" = "BFI-E",
                               "BFI-Part 2" = "BFI-A",
                               "NFCC, Part 1" = "NFCC-PDC",
                               "NFCC, Part 2" = "NFCC-AO")) %>%
  full_join(joiner_data_frame, by = "Scale") %>%
  select(-Scale) %>%
  rename(Scale = Scales_all) 

```

## Scale descriptives

Items per scale

```{r}

additional_scale_data %>%
  summarize(mean = round(mean(Items), 1),
            sd = round(sd(Items), 1),
            min = round(min(Items), 1),
            max = round(max(Items), 1)) %>%
  gather() %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

## Models

```{r}

bfi_e_model <- "E =~ bfi_e1 + bfi_e2 + bfi_e3 + bfi_e4 + bfi_e5 + bfi_e6 + bfi_e7 + bfi_e8" 

bfi_c_model <- "C =~ bfi_c1 + bfi_c2 + bfi_c3 + bfi_c4 + bfi_c5 + bfi_c6 + bfi_c7 + bfi_c8 + bfi_c9" 

bfi_n_model <- "N =~ bfi_n1 + bfi_n2 + bfi_n3 + bfi_n4 + bfi_n5 + bfi_n6 + bfi_n7 + bfi_n8" 

bfi_a_model <- "A =~ bfi_a1 + bfi_a2 + bfi_a3 + bfi_a4 + bfi_a5 + bfi_a6 + bfi_a7 + bfi_a8 + bfi_a9" 

bfi_o_model <- "O =~ bfi_o1 + bfi_o2 + bfi_o3 + bfi_o4 + bfi_o5 + bfi_o6 + bfi_o7 + bfi_o8 + bfi_o9 + bfi_o10" 

bidr_im_model <- "IM =~ bidr_im1 + bidr_im2 + bidr_im3 + bidr_im4 + bidr_im5 + bidr_im6 + bidr_im7 + 
                        bidr_im8 + bidr_im9 + bidr_im10 + bidr_im11 + bidr_im12 + bidr_im13 + bidr_im14 + 
                        bidr_im15 + bidr_im16 + bidr_im17 + bidr_im18" 

bidr_sde_model <- "SDE =~ bidr_sde1 + bidr_sde2 + bidr_sde3 + bidr_sde4 + bidr_sde5 + bidr_sde6 + bidr_sde7 +
                          bidr_sde8 + bidr_sde9 + bidr_sde10 + bidr_sde11 + bidr_sde12 + bidr_sde13 + 
                          bidr_sde14 + bidr_sde15 + bidr_sde16 + bidr_sde17 + bidr_sde18" 

bjw_model <- "BJW =~ bjw1 + bjw2 + bjw3 + bjw4 + bjw5 + bjw6" 

brs_model <- "BRS =~ brs1 + brs2 + brs3 + brs4 + brs5 + brs6 + brs7 + brs8 + 
                     brs9 + brs10 + brs11 + brs12 + brs13 + brs14 + brs15 + brs16" 

he_model <- "HE =~ he1 + he2 + he3 + he4 + he5 + he6 + he7 + he8 + he9 + he10" 

icat_o_model <- "ICAT_O =~ icat_o1 + icat_o2 + icat_o3 + icat_o4 + icat_o5 + icat_o6 + icat_o7 + icat_o8 + icat_o9" 

icat_s_model <- "ICAT_S =~ icat_s1 + icat_s2 + icat_s3 + icat_s4 + icat_s5 + icat_s6 + icat_s7 + icat_s8 + icat_s9" 

nfc_model <- "NFC =~ nfc1 + nfc2 + nfc3 + nfc4 + nfc5 + nfc6 + nfc7 + nfc8 + nfc9 + 
                     nfc10 + nfc11 + nfc12 + nfc13 + nfc14 + nfc15 + nfc16 + nfc17 + nfc18" 

nfcc_p_model <- "P =~ nfcc_p1 + nfcc_p2 + nfcc_p3 + nfcc_p4 + nfcc_p5 + nfcc_p6 + nfcc_p7 + nfcc_p8" 

nfcc_d_model <- "D =~ nfcc_d1 + nfcc_d2 + nfcc_d3 + nfcc_d4 + nfcc_d5 + nfcc_d6 + nfcc_d7" 

nfcc_c_model <- "C =~ nfcc_c1 + nfcc_c2 + nfcc_c3 + nfcc_c4 + nfcc_c5 + nfcc_c6 + nfcc_c7 + nfcc_c8" 

nfcc_a_model <- "A =~ nfcc_a1 + nfcc_a2 + nfcc_a3 + nfcc_a4 + nfcc_a5 + 
                      nfcc_a6 + nfcc_a7 + nfcc_a8 + nfcc_a9"

nfcc_o_model <- "O =~ nfcc_o1 + nfcc_o2 + nfcc_o3 + nfcc_o4 + nfcc_o5 +
                      nfcc_o6 + nfcc_o7 + nfcc_o8 + nfcc_o9 + nfcc_o10" 

pe_model <- "PE =~ pe1 + pe2 + pe3 + pe4 + pe5 + pe6 + pe7 + pe8 + pe9 + pe10 + pe11" 

pns_model <- "PNS =~ pns1 + pns2 + pns3 + pns4 + pns5 + pns6 + pns7 + pns8 + pns9 + pns10 + pns11 + pns12" 

rse_model <- "RSE =~ rse1 + rse2 + rse3 + rse4 + rse5 + rse6 + rse7 + rse8 + rse9 + rse10" 

rwa_model <- "RWA =~ rwa1 + rwa2 + rwa3 + rwa4 + rwa5 + rwa6 + rwa7 + rwa8 + rwa9 + rwa10 + 
                     rwa11 + rwa12 + rwa13 + rwa14 + rwa15 + rwa16 + rwa17 + rwa18 + rwa19 + rwa20" 

sdo_model <- "SDO =~ sdo1 + sdo2 + sdo3 + sdo4 + sdo5 + sdo6 + sdo7 + sdo8 + sdo9 + sdo10 + sdo11 + sdo12" 

sm_model <- "SM =~ sm1 + sm2 + sm3 + sm4 + sm5 + sm6 + sm7 + sm8 + sm9 + 
                   sm10 + sm11 + sm12 + sm13 + sm14 + sm15 + sm16 + sm17 + sm18" 

soc_ic_model <- "IC =~ soc_ic1 + soc_ic2 + soc_ic3 + soc_ic4 + soc_ic5 + 
                       soc_ic6 + soc_ic7 + soc_ic8 + soc_ic9 + soc_ic10" 

soc_pe_model <- "PE =~ soc_pe1 + soc_pe2 + soc_pe3 + soc_pe4 + soc_pe5 + 
                       soc_pe6 + soc_pe7 + soc_pe8 + soc_pe9 + soc_pe10" 

distinct(trimmed_data, nfcc_a10)

```

# Demographics

```{r}

trimmed_data %>%
  count() %>%
  rename(`N unique experimental sessions` = n) %>%
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

trimmed_data %>%
  select(user_id, session_id) %>%
  group_by(user_id) %>%
  summarize(n = n()) %>%
  summarize(mean_sessions = mean(n),
            median_sessions = median(n),
            sd_sessions = sd(n)) %>%
  round_df(2) %>%
  gather() %>%
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

demographics_temp <- trimmed_first_timepoint_per_user_per_scale %>%
  mutate(sex = recode(sex,
                      "f" = 1,
                      "m" = 2)) %>%
  group_by(user_id) %>%
  # given repeat presentations
  summarize(mean_age_across_participations = mean(age),
            sex = mean(sex)) %>%
  ungroup() %>%
  mutate(sex = recode(sex,
                      "1" = "f",
                      "2" = "m"))

demographics_temp %>%
  count() %>%
  rename(`N unique participants` = n) %>%
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

demographics_temp %>%
  count(sex) %>%
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

demographics_temp %>%
  summarise(age_mean = mean(mean_age_across_participations),
            age_median = median(mean_age_across_participations),
            age_sd = sd(mean_age_across_participations)) %>%
  round_df(2) %>%
  gather() %>%
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

# Structural validity analyses

## Distributions

```{r}

# scales
trimmed_first_timepoint_per_user_per_scale %>%
  filter(!individual_differences_measure %in% c("BFI-Part 1",
                                                "BFI-Part 2",
                                                "NFCC, Part 1",
                                                "NFCC, Part 2")) %>%
  ggplot() + 
  geom_density(aes(individual_differences_sum_score)) +
  facet_wrap(~individual_differences_measure, scales = "free")

# subscales where applicable
trimmed_first_timepoint_per_user_per_scale %>%
  select(session_id, 
         BFI_E_subscale, BFI_C_subscale, BFI_N_subscale, BFI_A_subscale, BFI_O_subscale, 
         NFCC_P_subscale, NFCC_D_subscale, NFCC_C_subscale, NFCC_O_subscale, NFCC_A_subscale) %>%
  gather(key = subscale, value = score, c(BFI_E_subscale, BFI_C_subscale, BFI_N_subscale, BFI_A_subscale, BFI_O_subscale, 
                                          NFCC_P_subscale, NFCC_D_subscale, NFCC_C_subscale, NFCC_O_subscale, NFCC_A_subscale)) %>%
  na.omit() %>%
  ggplot() + 
  geom_density(aes(score)) +
  facet_wrap(~subscale, scales = "free")

```

```{r}

## distribution info
distributions_auto <- function(data, scale_name) {
  require(moments)
  require(plotrix)
  data %>%
    mutate(sum = rowSums(.)) %>%
    dplyr::select(sum) %>%
    summarize(M = round(mean(sum, na.rm = TRUE), 2),
              SE = round(std.error(sum, na.rm = TRUE), 2),
              SD = round(sd(sum, na.rm = TRUE), 2),
              Skewness = round(skewness(sum), 2),
              Kurtosis = round(kurtosis(sum), 2)) %>%
    mutate(Scale = scale_name)
}

bfi_e_dist    <- bfi_e_data    %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Big 5 Inventory - E")
bfi_c_dist    <- bfi_c_data    %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Big 5 Inventory - C")
bfi_n_dist    <- bfi_n_data    %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Big 5 Inventory - N")
bfi_a_dist    <- bfi_a_data    %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Big 5 Inventory - A")
bfi_o_dist    <- bfi_o_data    %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Big 5 Inventory - O")
bidr_im_dist  <- bidr_im_data  %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Balanced Inventory of Desirable Responding - Impression Management")
bidr_sde_dist <- bidr_sde_data %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Balanced Inventory of Desirable Responding - Self Deception")
bjw_dist      <- bjw_data      %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Belief in a Just World")
brs_dist      <- brs_data      %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Bayesian Racism")
he_dist       <- he_data       %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Humanitarianism-Egalitarianism")
icat_o_dist   <- icat_o_data   %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Intuitions about Controllability and Awareness of Thoughts - Others")
icat_s_dist   <- icat_s_data   %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Intuitions about Controllability and Awareness of Thoughts - Self")
nfc_dist      <- nfc_data      %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Need for Cognition")
nfcc_a_dist   <- nfcc_a_data   %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Need for Cognitive Closure - A")
nfcc_o_dist   <- nfcc_o_data   %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Need for Cognitive Closure - O")
nfcc_p_dist   <- nfcc_p_data   %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Need for Cognitive Closure - P")
nfcc_d_dist   <- nfcc_d_data   %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Need for Cognitive Closure - D")
nfcc_c_dist   <- nfcc_c_data   %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Need for Cognitive Closure - C")
pe_dist       <- pe_data       %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Protestant Ethic")
pns_dist      <- pns_data      %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Personal Need for Structure")
rse_dist      <- rse_data      %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Rosenberg Self-Esteem")
rwa_dist      <- rwa_data      %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Ring-Wing Authoritarianism")
sdo_dist      <- sdo_data      %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Social Dominance Orientation")
sm_dist       <- sm_data       %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Self-Monitoring")
soc_ic_dist   <- soc_ic_data   %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Spheres of Control - Interpersonal Control")
soc_pe_dist   <- soc_pe_data   %>% dplyr::select(-age, -sex) %>% distributions_auto(., scale_name = "Spheres of Control - Personal Efficacy")

dist_results <- rbind(bfi_e_dist, bfi_c_dist, bfi_n_dist, bfi_a_dist, bfi_o_dist,
                      bidr_im_dist, bidr_sde_dist, bjw_dist, brs_dist,
                      he_dist, icat_o_dist, icat_s_dist, nfc_dist, 
                      nfcc_a_dist, nfcc_o_dist, nfcc_p_dist, nfcc_d_dist, nfcc_c_dist,
                      pe_dist, pns_dist, rse_dist, rwa_dist, sdo_dist, sm_dist, soc_ic_dist, soc_pe_dist)

# remove redundant objects to keep the environment tidy
rm(bfi_e_dist, bfi_c_dist, bfi_n_dist, bfi_a_dist, bfi_o_dist,
   bidr_im_dist, bidr_sde_dist, bjw_dist, brs_dist,
   he_dist, icat_o_dist, icat_s_dist, nfc_dist, 
   nfcc_a_dist, nfcc_o_dist, nfcc_p_dist, nfcc_d_dist, nfcc_c_dist,
   pe_dist, pns_dist, rse_dist, rwa_dist, sdo_dist, sm_dist, soc_ic_dist, soc_pe_dist)

```

## Internal consistency

```{r}

# needed for both consistency and cfa analyses
fit_cfa <- function(data, model) {
  require(lavaan)
  require(tidyverse)

  data %>%
    dplyr::select(-sex, -age) %>%
    cfa(model,
        data = .,
        order = c("1", "2", "3", "4", "5", "6"),
        estimator = "WLSMV")  # can notionally change this to Maximum Likelihood (ML) but produces worse fits across measures
}

```

```{r}

# # NB Bootstrapping of the CIs takes time (30+ mins), so the results have been saved to disk to save others time. Uncomment the below code to redo the bootstrapping.


n_boots <- 1

# NB the below code isn't as elegant as I'd like, but works just fine. `model` should be passed as an argument among the three nested functions, but I couldn't work out how to get purrr::map() to take an argument for the function it applies to the bootstraps. Instead, model is defined as a global variable before each estimate_reliability() call. This variable scoping is fine statistically, but represents suboptimal coding afaik. 

# helper function
bootstrap_reliability_helper <- function(split, ...) {

  require(lavaan)
  require(semTools)
  require(tidyverse)

  fit_cfa(analysis(split), model) %>%
    reliability() %>%
    as.data.frame() %>%
    rownames_to_column(var = "metric") %>%
    select(metric, total) %>%
    filter(metric %in% c("alpha",
                         "omega2",
                         "omega3")) %>%
    mutate(metric = recode(metric,
                           "alpha" = "alpha",
                           "omega2" = "omega_t",
                           "omega3" = "omega_h"))

}

# apply bootstrapping, then extract coefficients via percentile method
estimate_reliability <- function(data, scale, ...) {

  require(purrr)
  require(rsample)
  require(tidyverse)
  require(timesavers)

  # create bootstraps using out of bag method. makes a df with values that are collapsed dfs.
  boot_samples <- data %>%
    bootstraps(., times = n_boots)

  # apply to each bootstrap
  boots <- boot_samples %>%
    mutate(reliability_results = map(splits, bootstrap_reliability_helper)) %>%
    unnest(reliability_results)

  # find CIs using percentile method
  boot_estimates <- boots %>%
    group_by(metric) %>%
    summarize(median   = quantile(total, 0.500),
              ci_lower = quantile(total, 0.025),
              ci_upper = quantile(total, 0.975)) %>%
    round_df(3) %>%
    mutate(Scale = scale)

  return(boot_estimates)
}

model <- bfi_e_model
consistency_bfi_e    <- estimate_reliability(bfi_e_data,    "Big 5 Inventory - E")

model <- bfi_c_model
consistency_bfi_c    <- estimate_reliability(bfi_c_data,    "Big 5 Inventory - C")

model <- bfi_n_model
consistency_bfi_n    <- estimate_reliability(bfi_n_data,    "Big 5 Inventory - N")

model <- bfi_a_model
consistency_bfi_a    <- estimate_reliability(bfi_a_data,    "Big 5 Inventory - A")

model <- bfi_o_model
consistency_bfi_o    <- estimate_reliability(bfi_o_data,    "Big 5 Inventory - O")

model <- bidr_im_model
consistency_bidr_im  <- estimate_reliability(bidr_im_data,  "Balanced Inventory of Desirable Responding - Impression Management")

model <- bidr_sde_model
consistency_bidr_sde <- estimate_reliability(bidr_sde_data, "Balanced Inventory of Desirable Responding - Self Deception")

model <- bjw_model
consistency_bjw      <- estimate_reliability(bjw_data,      "Belief in a Just World: General Just World Scale")

model <- brs_model
consistency_brs      <- estimate_reliability(brs_data,      "Bayesian Racism")

model <- he_model
consistency_he       <- estimate_reliability(he_data,       "Humanitarianism-Egalitarianism")

model <- icat_o_model
consistency_icat_o   <- estimate_reliability(icat_o_data,   "Intuitions about Controllability and Awareness of Thoughts - Others")

model <- icat_s_model
consistency_icat_s   <- estimate_reliability(icat_s_data,   "Intuitions about Controllability and Awareness of Thoughts - Self")

model <- nfc_model
consistency_nfc      <- estimate_reliability(nfc_data,      "Need for Cognition")

model <- nfcc_a_model
consistency_nfcc_a   <- estimate_reliability(nfcc_a_data,   "Need for Cognitive Closure - A")

model <- nfcc_o_model
consistency_nfcc_o   <- estimate_reliability(nfcc_o_data,   "Need for Cognitive Closure - O")

model <- nfcc_p_model
consistency_nfcc_p   <- estimate_reliability(nfcc_p_data,   "Need for Cognitive Closure - P")

model <- nfcc_d_model
consistency_nfcc_d   <- estimate_reliability(nfcc_d_data,   "Need for Cognitive Closure - D")

model <- nfcc_c_model
consistency_nfcc_c   <- estimate_reliability(nfcc_c_data,   "Need for Cognitive Closure - C")

model <- pe_model
consistency_pe       <- estimate_reliability(pe_data,       "Protestant Ethic")

model <- pns_model
consistency_pns      <- estimate_reliability(pns_data,      "Personal Need for Structure")

model <- rse_model
consistency_rse      <- estimate_reliability(rse_data,      "Rosenberg Self-Esteem")

model <- rwa_model
consistency_rwa      <- estimate_reliability(rwa_data,      "Ring-Wing Authoritarianism")

model <- sdo_model
consistency_sdo      <- estimate_reliability(sdo_data,      "Social Dominance Orientation")

model <- sm_model
consistency_sm       <- estimate_reliability(sm_data,       "Self-Monitoring")

model <- soc_ic_model
consistency_soc_ic   <- estimate_reliability(soc_ic_data,   "Spheres of Control - Interpersonal Control")

model <- soc_pe_model
consistency_soc_pe   <- estimate_reliability(soc_pe_data,   "Spheres of Control - Personal Efficacy")

consistency_estimates_temp <- bind_rows(consistency_bfi_e,
                                        consistency_bfi_c,
                                        consistency_bfi_n,
                                        consistency_bfi_a,
                                        consistency_bfi_o,
                                        consistency_bidr_im,
                                        consistency_bidr_sde,
                                        consistency_bjw,
                                        consistency_brs,
                                        consistency_he,
                                        consistency_icat_o,
                                        consistency_icat_s,
                                        consistency_nfc,
                                        consistency_nfcc_a,
                                        consistency_nfcc_o,
                                        consistency_nfcc_p,
                                        consistency_nfcc_d,
                                        consistency_nfcc_c,
                                        consistency_pe,
                                        consistency_pns,
                                        consistency_rse,
                                        consistency_rwa,
                                        consistency_sdo,
                                        consistency_sm,
                                        consistency_soc_ic,
                                        consistency_soc_pe)

consistency_estimates_alpha <- consistency_estimates_temp %>%
  filter(metric == "alpha") %>%
  select(-metric) %>%
  rename(alpha = median,
         alpha_ci_lower = ci_lower,
         alpha_ci_upper = ci_upper)

consistency_estimates_omega_t <- consistency_estimates_temp %>%
  filter(metric == "omega_t") %>%
  select(-metric) %>%
  rename(omega_t = median,
         omega_t_ci_lower = ci_lower,
         omega_t_ci_upper = ci_upper)

consistency_estimates_omega_h <- consistency_estimates_temp %>%
  filter(metric == "omega_h") %>%
  select(-metric) %>%
  rename(omega_h = median,
         omega_h_ci_lower = ci_lower,
         omega_h_ci_upper = ci_upper)

consistency_results <- consistency_estimates_alpha %>%
  left_join(consistency_estimates_omega_t, by = "Scale") %>%
  left_join(consistency_estimates_omega_h, by = "Scale")

# remove redundant objects to keep the environment tidy
rm(consistency_estimates_alpha, consistency_estimates_omega_t, consistency_estimates_omega_h,
   consistency_bfi_e, consistency_bfi_c, consistency_bfi_n, consistency_bfi_a,
   consistency_bfi_o, consistency_bidr_im, consistency_bidr_sde, consistency_bjw, consistency_brs, consistency_he,
   consistency_icat_o, consistency_icat_s, consistency_nfc, consistency_nfcc_a, consistency_nfcc_o, 
   consistency_nfcc_p, consistency_nfcc_d, consistency_nfcc_c, consistency_pe, consistency_pns,
   consistency_rse, consistency_rwa, consistency_sdo, consistency_sm, consistency_soc_ic, consistency_soc_pe)

```

```{r}
#save(consistency_results, file = "results/consistency_results.RData")
load("results/consistency_results.RData")
```

## Test-retest reliability

### Dependability

```{r}

dependability_data <- two_timepoint_scores %>%
  filter(days_to_followup < 1/24)  # retest within an hour

# # n per scale
n_per_scale_dependability <- dependability_data %>%
  count(individual_differences_measure) %>%
  rename(Scale = individual_differences_measure,
         `Test-retest dependability n` = n)

pearson_r_estimate <- function(data, Scale){
  require(tidyverse)
  require(psych)
  
  res <- data %>%
    filter(individual_differences_measure == Scale) %>%
    select(individual_differences_sum_score_t1, individual_differences_sum_score_t2) %>%
    cor.ci(n.iter = 1000, method = "pearson", plot = FALSE)
  
  results <-
    data.frame(Scale = Scale,
               pearson_r = res$means,
               pearson_r_ci_lwr = res$ci$low.e,
               pearson_r_ci_upr = res$ci$up.e) %>%
    round_df(3)
  
  return(results)
}

dependability_results <-
  rbind(pearson_r_estimate(data = dependability_data, Scale = "BFI_E"),
        pearson_r_estimate(data = dependability_data, Scale = "BFI_C"),
        pearson_r_estimate(data = dependability_data, Scale = "BFI_N"),
        pearson_r_estimate(data = dependability_data, Scale = "BFI_A"),
        pearson_r_estimate(data = dependability_data, Scale = "BFI_O"),
        pearson_r_estimate(data = dependability_data, Scale = "BIDR-IM"),
        pearson_r_estimate(data = dependability_data, Scale = "BIDR-SDE"),
        pearson_r_estimate(data = dependability_data, Scale = "BJW"),
        pearson_r_estimate(data = dependability_data, Scale = "BRS"),
        pearson_r_estimate(data = dependability_data, Scale = "HE"),
        pearson_r_estimate(data = dependability_data, Scale = "ICAT-O"),
        pearson_r_estimate(data = dependability_data, Scale = "ICAT-S"),
        pearson_r_estimate(data = dependability_data, Scale = "NFC"),
        #pearson_r_estimate(data = dependability_data, Scale = "NFCC_A"),
        pearson_r_estimate(data = dependability_data, Scale = "NFCC_O"),
        pearson_r_estimate(data = dependability_data, Scale = "NFCC_P"),
        pearson_r_estimate(data = dependability_data, Scale = "NFCC_D"),
        pearson_r_estimate(data = dependability_data, Scale = "NFCC_C"),
        pearson_r_estimate(data = dependability_data, Scale = "PE"),
        pearson_r_estimate(data = dependability_data, Scale = "PNS"),
        pearson_r_estimate(data = dependability_data, Scale = "RSE"),
        pearson_r_estimate(data = dependability_data, Scale = "RWA"),
        pearson_r_estimate(data = dependability_data, Scale = "SDO"),
        pearson_r_estimate(data = dependability_data, Scale = "SM"),
        pearson_r_estimate(data = dependability_data, Scale = "SOC-IC"),
        pearson_r_estimate(data = dependability_data, Scale = "SOC-PE")) %>%
  rename(`Test-retest dependability r` = pearson_r,
         `dependability r lower` = pearson_r_ci_lwr,
         `dependability r upper` = pearson_r_ci_upr) %>%
  full_join(n_per_scale_dependability, by = "Scale") 

```

### Stability

```{r}

stability_data <- two_timepoint_scores %>%
  filter(days_to_followup >= 1 & days_to_followup < 365)  # retest more than a day and less than a year later

# n per scale
n_per_scale_stability <- stability_data %>%
  count(individual_differences_measure) %>%
  rename(Scale = individual_differences_measure,
         `Test-retest dependability n` = n)

stability_results <-
  rbind(pearson_r_estimate(data = stability_data, Scale = "BFI_E"),
        pearson_r_estimate(data = stability_data, Scale = "BFI_C"),
        pearson_r_estimate(data = stability_data, Scale = "BFI_N"),
        pearson_r_estimate(data = stability_data, Scale = "BFI_A"),
        pearson_r_estimate(data = stability_data, Scale = "BFI_O"),
        pearson_r_estimate(data = stability_data, Scale = "BIDR-IM"),
        pearson_r_estimate(data = stability_data, Scale = "BIDR-SDE"),
        pearson_r_estimate(data = stability_data, Scale = "BJW"),
        pearson_r_estimate(data = stability_data, Scale = "BRS"),
        pearson_r_estimate(data = stability_data, Scale = "HE"),
        pearson_r_estimate(data = stability_data, Scale = "ICAT-O"),
        pearson_r_estimate(data = stability_data, Scale = "ICAT-S"),
        pearson_r_estimate(data = stability_data, Scale = "NFC"),
        #pearson_r_estimate(data = stability_data, Scale = "NFCC_A"),
        pearson_r_estimate(data = stability_data, Scale = "NFCC_O"),
        pearson_r_estimate(data = stability_data, Scale = "NFCC_P"),
        pearson_r_estimate(data = stability_data, Scale = "NFCC_D"),
        pearson_r_estimate(data = stability_data, Scale = "NFCC_C"),
        pearson_r_estimate(data = stability_data, Scale = "PE"),
        pearson_r_estimate(data = stability_data, Scale = "PNS"),
        pearson_r_estimate(data = stability_data, Scale = "RSE"),
        pearson_r_estimate(data = stability_data, Scale = "RWA"),
        pearson_r_estimate(data = stability_data, Scale = "SDO"),
        pearson_r_estimate(data = stability_data, Scale = "SM"),
        pearson_r_estimate(data = stability_data, Scale = "SOC-IC"),
        pearson_r_estimate(data = stability_data, Scale = "SOC-PE")) %>%
  rename(`Test-retest stability r` = pearson_r,
         `stability r lower` = pearson_r_ci_lwr,
         `stability r upper` = pearson_r_ci_upr) %>%
  full_join(n_per_scale_stability, by = "Scale")

```

## CFA fits

```{r}

## fit a CFA and return its model fit statistics
cfa_fit_metrics <- function(fit, scale) {
  
  require(lavaan)
  require(tidyverse)
  
  # fit statistics
  fit_stats <- data.frame(estimate = fitMeasures(fit)) %>%
    rownames_to_column(var = "metric") %>%
    filter(metric %in% c("chisq", "df", "pvalue", "srmr", "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "cfi", "tli")) %>%
    spread(metric, estimate) %>%
    mutate(Scale = scale,
           pvalue = ifelse(pvalue < .0001, "< .0001", as.character(round(pvalue, 4))),
           "chisq/df"  = round(chisq/df, 1),
           cfa_test = ifelse(srmr <= .09 & cfi >= .95 & tli >= .95 & rmsea <= .06, "Good",
                                ifelse(srmr <= .09 & (cfi >= .95 | tli >= .95 | rmsea <= .06), "Mixed", "Poor")),
           cfa_test = fct_relevel(cfa_test, "Good", "Mixed", "Poor"))
    
  return(fit_stats)
}

cfi_fit_results <- 
  bind_rows(cfa_fit_metrics(fit_cfa(bfi_e_data,    bfi_e_model),    scale = "Big 5 Inventory - E"),
            cfa_fit_metrics(fit_cfa(bfi_c_data,    bfi_c_model),    scale = "Big 5 Inventory - C"),
            cfa_fit_metrics(fit_cfa(bfi_n_data,    bfi_n_model),    scale = "Big 5 Inventory - N"),
            cfa_fit_metrics(fit_cfa(bfi_a_data,    bfi_a_model),    scale = "Big 5 Inventory - A"),
            cfa_fit_metrics(fit_cfa(bfi_o_data,    bfi_o_model),    scale = "Big 5 Inventory - O"),
            cfa_fit_metrics(fit_cfa(bidr_im_data,  bidr_im_model),  scale = "Balanced Inventory of Desirable Responding - Impression Management"),
            cfa_fit_metrics(fit_cfa(bidr_sde_data, bidr_sde_model), scale = "Balanced Inventory of Desirable Responding - Self Deception"),
            cfa_fit_metrics(fit_cfa(bjw_data,      bjw_model),      scale = "Belief in a Just World: General Just World Scale"),
            cfa_fit_metrics(fit_cfa(brs_data,      brs_model),      scale = "Bayesian Racism"),
            cfa_fit_metrics(fit_cfa(he_data,       he_model),       scale = "Humanitarianism-Egalitarianism"),
            cfa_fit_metrics(fit_cfa(icat_o_data,   icat_o_model),   scale = "Intuitions about Controllability and Awareness of Thoughts - Others"),
            cfa_fit_metrics(fit_cfa(icat_s_data,   icat_s_model),   scale = "Intuitions about Controllability and Awareness of Thoughts - Self"),
            cfa_fit_metrics(fit_cfa(nfc_data,      nfc_model),      scale = "Need for Cognition"),
            cfa_fit_metrics(fit_cfa(nfcc_a_data,   nfcc_a_model),   scale = "Need for Cognitive Closure - O"),
            cfa_fit_metrics(fit_cfa(nfcc_o_data,   nfcc_o_model),   scale = "Need for Cognitive Closure - A"),
            cfa_fit_metrics(fit_cfa(nfcc_p_data,   nfcc_p_model),   scale = "Need for Cognitive Closure - P"),
            cfa_fit_metrics(fit_cfa(nfcc_d_data,   nfcc_d_model),   scale = "Need for Cognitive Closure - D"),
            cfa_fit_metrics(fit_cfa(nfcc_c_data,   nfcc_c_model),   scale = "Need for Cognitive Closure - C"),
            cfa_fit_metrics(fit_cfa(pe_data,       pe_model),       scale = "Protestant Ethic"),
            cfa_fit_metrics(fit_cfa(pns_data,      pns_model),      scale = "Personal Need for Structure"),
            cfa_fit_metrics(fit_cfa(rse_data,      rse_model),      scale = "Rosenberg Self-Esteem"),
            cfa_fit_metrics(fit_cfa(rwa_data,      rwa_model),      scale = "Ring-Wing Authoritarianism"),
            cfa_fit_metrics(fit_cfa(sdo_data,      sdo_model),      scale = "Social Dominance Orientation"),
            cfa_fit_metrics(fit_cfa(sm_data,       sm_model),       scale = "Self-Monitoring"),
            cfa_fit_metrics(fit_cfa(soc_ic_data,   soc_ic_model),   scale = "Spheres of Control - Interpersonal Control"),
            cfa_fit_metrics(fit_cfa(soc_pe_data,   soc_pe_model),   scale = "Spheres of Control - Personal Efficacy")) %>%
  round_df(3) %>%
  # join other scale data in
  left_join(n_per_scale, by = "Scale") %>% 
  left_join(additional_scale_data, by = "Scale")

```

## Measurement Invariance

Between groups: gender and median age. 

Tests of measurement invariance (configural, metric, and scalar) using the cutoffs on the change in goodness-of-fit indices rather than a likelihood ratio test, which is highly senstive to sample size (Cheung & Rensvold, 2002). Cutoffs for configural invariance provided by Hu and Bentler (1999: same criteria as CFA fits above) and for metric and scalar invariance provided by Cheung & Rensvold (2002: ΔRMSEA <= 0.01 & ΔCLI <= -0.015; see also Chen, 2007 for very similar reccomendations). MI tests are conducted using the same methods as the CFAs: by assuming data is ordinal (e.g., likert data) using the distribution free DWLS estimator plus robust effect size estimates (i.e., estimator = "WLSMV").

```{r include=FALSE}

# i originally used semTools::measurementInvarianceCat() but it gave convergence issues with many models. it is also now depreciated. the following post suggested this has been observed before (https://groups.google.com/forum/#!topic/lavaan/aGCVepFrcCs). to maintain a uniform strategy across all scales, i changed to a manual CFA contraint strategy below.

mi_via_cutoffs <- function(data, model, scale, group) {
  
  # dependencies
  require(lavaan)
  require(tidyverse)
  require(semTools)
  require(timesavers)
  
  # fit the configural model 
  fit_configural <- data %>%
    cfa(model = model,
        data  = .,
        order = c("1", "2", "3", "4", "5", "6"),
        estimator = "WLSMV",
        group = group)
  
  # constrain slopes
  fit_metric <- data %>%
    cfa(model = model,
        data  = .,
        order = c("1", "2", "3", "4", "5", "6"),
        estimator = "WLSMV",
        group = group,
        group.equal = "loadings")
  
  # constrain intercepts
  fit_scalar <- data %>%
    cfa(model = model,
        data  = .,
        order = c("1", "2", "3", "4", "5", "6"),
        estimator = "WLSMV",
        group = group,
        group.equal = c("loadings", "intercepts"))
  
  # summarize these cfa fit indices, and their change across nested models
  results <- compareFit(fit_configural, fit_metric, fit_scalar, nested = TRUE) %>%
    summary()
  
  fit_indices <- results$fit.indices %>%
    rownames_to_column(var = "test") %>%
    mutate(MI_config = ifelse(srmr <= .09 & cfi.scaled >= .95 & 
                                tli.scaled >= .95 & 
                                rmsea.scaled <= .06, "Good",
                              ifelse(srmr <= .09 & (cfi.scaled >= .95 | 
                                                      tli.scaled >= .95 | 
                                                      rmsea.scaled <= .06), "Mixed", "Poor")),
           MI_config = ifelse(test == "fit_configural", MI_config, NA),
           pvalue.scaled = as.character(ifelse(pvalue.scaled < .0001, "< .0001", round(pvalue.scaled, 4)))) %>%
    round_df(3) %>%
    mutate(Scale = scale,
           group = group)
  
  fit_deltas <- results$fit.diff %>%
    rownames_to_column(var = "test") %>%
    mutate(MI_delta = ifelse(rmsea.scaled > 0.01 | cfi.scaled < -0.015, "Failed", "Passed")) %>%
    round_df(3) %>%
    mutate(Scale = scale,
           group = group)
  
  # return results as a list of data frames, including the fitted models
  return(list(fit_indices    = fit_indices,
              fit_deltas     = fit_deltas))
  
}

# mi for gender
MI_sex_bfi_e    <- mi_via_cutoffs(data = bfi_e_data,    model = bfi_e_model,    scale = "bfi_e",    group = "sex")
MI_sex_bfi_c    <- mi_via_cutoffs(data = bfi_c_data,    model = bfi_c_model,    scale = "bfi_c",    group = "sex")
MI_sex_bfi_n    <- mi_via_cutoffs(data = bfi_n_data,    model = bfi_n_model,    scale = "bfi_n",    group = "sex")
MI_sex_bfi_a    <- mi_via_cutoffs(data = bfi_a_data,    model = bfi_a_model,    scale = "bfi_a",    group = "sex")
MI_sex_bfi_o    <- mi_via_cutoffs(data = bfi_o_data,    model = bfi_o_model,    scale = "bfi_o",    group = "sex")
MI_sex_bidr_im  <- mi_via_cutoffs(data = bidr_im_data,  model = bidr_im_model,  scale = "bidr_im",  group = "sex")
MI_sex_bidr_sde <- mi_via_cutoffs(data = bidr_sde_data, model = bidr_sde_model, scale = "bidr_sde", group = "sex")
MI_sex_bjw      <- mi_via_cutoffs(data = bjw_data,      model = bjw_model,      scale = "bjw",      group = "sex")
MI_sex_brs      <- mi_via_cutoffs(data = brs_data,      model = brs_model,      scale = "brs",      group = "sex")
MI_sex_he       <- mi_via_cutoffs(data = he_data,       model = he_model,       scale = "he",       group = "sex")
MI_sex_icat_o   <- mi_via_cutoffs(data = icat_o_data,   model = icat_o_model,   scale = "icat_o",   group = "sex")
MI_sex_icat_s   <- mi_via_cutoffs(data = icat_s_data,   model = icat_s_model,   scale = "icat_s",   group = "sex")
MI_sex_nfc      <- mi_via_cutoffs(data = nfc_data,      model = nfc_model,      scale = "nfc",      group = "sex")
MI_sex_nfcc_a   <- mi_via_cutoffs(data = nfcc_a_data,   model = nfcc_a_model,   scale = "nfcc_a",   group = "sex")
MI_sex_nfcc_o   <- mi_via_cutoffs(data = nfcc_o_data,   model = nfcc_o_model,   scale = "nfcc_o",   group = "sex")
MI_sex_nfcc_p   <- mi_via_cutoffs(data = nfcc_p_data,   model = nfcc_p_model,   scale = "nfcc_p",   group = "sex")
MI_sex_nfcc_d   <- mi_via_cutoffs(data = nfcc_d_data,   model = nfcc_d_model,   scale = "nfcc_d",   group = "sex")
MI_sex_nfcc_c   <- mi_via_cutoffs(data = nfcc_c_data,   model = nfcc_c_model,   scale = "nfcc_c",   group = "sex")
MI_sex_pe       <- mi_via_cutoffs(data = pe_data,       model = pe_model,       scale = "pe",       group = "sex")
MI_sex_pns      <- mi_via_cutoffs(data = pns_data,      model = pns_model,      scale = "pns",      group = "sex")
MI_sex_rse      <- mi_via_cutoffs(data = rse_data,      model = rse_model,      scale = "rse",      group = "sex")
MI_sex_rwa      <- mi_via_cutoffs(data = rwa_data,      model = rwa_model,      scale = "rwa",      group = "sex")
MI_sex_sdo      <- mi_via_cutoffs(data = sdo_data,      model = sdo_model,      scale = "sdo",      group = "sex")
MI_sex_sm       <- mi_via_cutoffs(data = sm_data,       model = sm_model,       scale = "sm",       group = "sex")
MI_sex_soc_ic   <- mi_via_cutoffs(data = soc_ic_data,   model = soc_ic_model,   scale = "soc_ic",   group = "sex")
MI_sex_soc_pe   <- mi_via_cutoffs(data = soc_pe_data,   model = soc_pe_model,   scale = "soc_pe",   group = "sex")

# mi for median age
MI_age_bfi_e    <- mi_via_cutoffs(data = bfi_e_data,    model = bfi_e_model,    scale = "bfi_e",    group = "age")
MI_age_bfi_c    <- mi_via_cutoffs(data = bfi_c_data,    model = bfi_c_model,    scale = "bfi_c",    group = "age")
MI_age_bfi_n    <- mi_via_cutoffs(data = bfi_n_data,    model = bfi_n_model,    scale = "bfi_n",    group = "age")
MI_age_bfi_a    <- mi_via_cutoffs(data = bfi_a_data,    model = bfi_a_model,    scale = "bfi_a",    group = "age")
MI_age_bfi_o    <- mi_via_cutoffs(data = bfi_o_data,    model = bfi_o_model,    scale = "bfi_o",    group = "age")
MI_age_bidr_im  <- mi_via_cutoffs(data = bidr_im_data,  model = bidr_im_model,  scale = "bidr_im",  group = "age")
MI_age_bidr_sde <- mi_via_cutoffs(data = bidr_sde_data, model = bidr_sde_model, scale = "bidr_sde", group = "age")
MI_age_bjw      <- mi_via_cutoffs(data = bjw_data,      model = bjw_model,      scale = "bjw",      group = "age")
MI_age_brs      <- mi_via_cutoffs(data = brs_data,      model = brs_model,      scale = "brs",      group = "age")
MI_age_he       <- mi_via_cutoffs(data = he_data,       model = he_model,       scale = "he",       group = "age")
MI_age_icat_o   <- mi_via_cutoffs(data = icat_o_data,   model = icat_o_model,   scale = "icat_o",   group = "age")
MI_age_icat_s   <- mi_via_cutoffs(data = icat_s_data,   model = icat_s_model,   scale = "icat_s",   group = "age")
MI_age_nfc      <- mi_via_cutoffs(data = nfc_data,      model = nfc_model,      scale = "nfc",      group = "age")
MI_age_nfcc_a   <- mi_via_cutoffs(data = nfcc_a_data,   model = nfcc_a_model,   scale = "nfcc_a",   group = "age")
MI_age_nfcc_o   <- mi_via_cutoffs(data = nfcc_o_data,   model = nfcc_o_model,   scale = "nfcc_o",   group = "age")
MI_age_nfcc_p   <- mi_via_cutoffs(data = nfcc_p_data,   model = nfcc_p_model,   scale = "nfcc_p",   group = "age")
MI_age_nfcc_d   <- mi_via_cutoffs(data = nfcc_d_data,   model = nfcc_d_model,   scale = "nfcc_d",   group = "age")
MI_age_nfcc_c   <- mi_via_cutoffs(data = nfcc_c_data,   model = nfcc_c_model,   scale = "nfcc_c",   group = "age")
MI_age_pe       <- mi_via_cutoffs(data = pe_data,       model = pe_model,       scale = "pe",       group = "age")
MI_age_pns      <- mi_via_cutoffs(data = pns_data,      model = pns_model,      scale = "pns",      group = "age")
MI_age_rse      <- mi_via_cutoffs(data = rse_data,      model = rse_model,      scale = "rse",      group = "age")
MI_age_rwa      <- mi_via_cutoffs(data = rwa_data,      model = rwa_model,      scale = "rwa",      group = "age")
MI_age_sdo      <- mi_via_cutoffs(data = sdo_data,      model = sdo_model,      scale = "sdo",      group = "age")
MI_age_sm       <- mi_via_cutoffs(data = sm_data,       model = sm_model,       scale = "sm",       group = "age")
MI_age_soc_ic   <- mi_via_cutoffs(data = soc_ic_data,   model = soc_ic_model,   scale = "soc_ic",   group = "age")
MI_age_soc_pe   <- mi_via_cutoffs(data = soc_pe_data,   model = soc_pe_model,   scale = "soc_pe",   group = "age")

# combine
## fit indices
MI_combined_fit_indicies <-
  rbind(MI_sex_bfi_e$fit_indices,
        MI_sex_bfi_c$fit_indices,
        MI_sex_bfi_n$fit_indices,
        MI_sex_bfi_a$fit_indices,
        MI_sex_bfi_o$fit_indices,
        MI_sex_bidr_im$fit_indices,
        MI_sex_bidr_sde$fit_indices,
        MI_sex_bjw$fit_indices,
        MI_sex_brs$fit_indices,
        MI_sex_he$fit_indices,
        MI_sex_icat_o$fit_indices,
        MI_sex_icat_s$fit_indices,
        MI_sex_nfc$fit_indices,
        MI_sex_nfcc_a$fit_indices,
        MI_sex_nfcc_o$fit_indices,
        MI_sex_nfcc_p$fit_indices,
        MI_sex_nfcc_d$fit_indices,
        MI_sex_nfcc_c$fit_indices,
        MI_sex_pe$fit_indices,
        MI_sex_pns$fit_indices,
        MI_sex_rse$fit_indices,
        MI_sex_rwa$fit_indices,
        MI_sex_sdo$fit_indices,
        MI_sex_sm$fit_indices,
        MI_sex_soc_ic$fit_indices,
        MI_sex_soc_pe$fit_indices,
        MI_age_bfi_e$fit_indices,
        MI_age_bfi_c$fit_indices,
        MI_age_bfi_n$fit_indices,
        MI_age_bfi_a$fit_indices,
        MI_age_bfi_o$fit_indices,
        MI_age_bidr_im$fit_indices,
        MI_age_bidr_sde$fit_indices,
        MI_age_bjw$fit_indices,
        MI_age_brs$fit_indices,
        MI_age_he$fit_indices,
        MI_age_icat_o$fit_indices,
        MI_age_icat_s$fit_indices,
        MI_age_nfc$fit_indices,
        MI_age_nfcc_a$fit_indices,
        MI_age_nfcc_o$fit_indices,
        MI_age_nfcc_p$fit_indices,
        MI_age_nfcc_d$fit_indices,
        MI_age_nfcc_c$fit_indices,
        MI_age_pe$fit_indices,
        MI_age_pns$fit_indices,
        MI_age_rse$fit_indices,
        MI_age_rwa$fit_indices,
        MI_age_sdo$fit_indices,
        MI_age_sm$fit_indices,
        MI_age_soc_ic$fit_indices,
        MI_age_soc_pe$fit_indices) %>%
  rename(df = df.scaled,
         fit_chisq_p_value = pvalue.scaled,
         chisq = chisq.scaled,
         srmr = srmr,
         cfi = cfi.scaled,
         tli = tli.scaled,
         rmsea = rmsea.scaled)

## change in fit indices
MI_combined_change_in_fit_indices <-
  rbind(MI_sex_bfi_e$fit_deltas,
        MI_sex_bfi_c$fit_deltas,
        MI_sex_bfi_n$fit_deltas,
        MI_sex_bfi_a$fit_deltas,
        MI_sex_bfi_o$fit_deltas,
        MI_sex_bidr_im$fit_deltas,
        MI_sex_bidr_sde$fit_deltas,
        MI_sex_bjw$fit_deltas,
        MI_sex_brs$fit_deltas,
        MI_sex_he$fit_deltas,
        MI_sex_icat_o$fit_deltas,
        MI_sex_icat_s$fit_deltas,
        MI_sex_nfc$fit_deltas,
        MI_sex_nfcc_a$fit_deltas,
        MI_sex_nfcc_o$fit_deltas,
        MI_sex_nfcc_p$fit_deltas,
        MI_sex_nfcc_d$fit_deltas,
        MI_sex_nfcc_c$fit_deltas,
        MI_sex_pe$fit_deltas,
        MI_sex_pns$fit_deltas,
        MI_sex_rse$fit_deltas,
        MI_sex_rwa$fit_deltas,
        MI_sex_sdo$fit_deltas,
        MI_sex_sm$fit_deltas,
        MI_sex_soc_ic$fit_deltas,
        MI_sex_soc_pe$fit_deltas,
        MI_age_bfi_e$fit_deltas,
        MI_age_bfi_c$fit_deltas,
        MI_age_bfi_n$fit_deltas,
        MI_age_bfi_a$fit_deltas,
        MI_age_bfi_o$fit_deltas,
        MI_age_bidr_im$fit_deltas,
        MI_age_bidr_sde$fit_deltas,
        MI_age_bjw$fit_deltas,
        MI_age_brs$fit_deltas,
        MI_age_he$fit_deltas,
        MI_age_icat_o$fit_deltas,
        MI_age_icat_s$fit_deltas,
        MI_age_nfc$fit_deltas,
        MI_age_nfcc_a$fit_deltas,
        MI_age_nfcc_o$fit_deltas,
        MI_age_nfcc_p$fit_deltas,
        MI_age_nfcc_d$fit_deltas,
        MI_age_nfcc_c$fit_deltas,
        MI_age_pe$fit_deltas,
        MI_age_pns$fit_deltas,
        MI_age_rse$fit_deltas,
        MI_age_rwa$fit_deltas,
        MI_age_sdo$fit_deltas,
        MI_age_sm$fit_deltas,
        MI_age_soc_ic$fit_deltas,
        MI_age_soc_pe$fit_deltas) %>%
  mutate(test = ifelse(test == "fit_metric - fit_configural", "fit_metric",
                       ifelse(test == "fit_scalar - fit_scalar", "fit_scalar", NA))) %>%
  rename(df_change = df.scaled,
         srmr_change = srmr,
         cfi_change = cfi.scaled,
         tli_change = tli.scaled,
         rmsea_change = rmsea.scaled)

measurement_invariance_full_results <- MI_combined_fit_indicies %>%
  left_join(MI_combined_change_in_fit_indices, by = c("Scale", "group", "test")) %>%
  arrange(Scale, group, test) %>%
  mutate(MI_test = ifelse(!is.na(MI_config), MI_config, MI_delta)) %>%
  select(Scale, group, test, 
         chisq, df, fit_chisq_p_value, cfi, tli, rmsea, srmr, 
         df_change, cfi_change, tli_change, rmsea_change, srmr_change, MI_test)


# summarize results in categorical terms
MI_results_temp_1 <- measurement_invariance_full_results %>%
  mutate(MI_test = ifelse(MI_test %in% c("Good", "Mixed"), "Passed",
                          ifelse(MI_test == "Poor", "Failed", MI_test))) %>%
  select(Scale, group, test, MI_test) %>%
  spread(test, MI_test) %>%
  mutate(MI_test = ifelse(fit_configural == "Passed" & 
                            fit_metric == "Passed" & 
                            fit_scalar == "Passed", "Passed", "Failed"),
         MI_test_failed = ifelse(fit_configural == "Failed", "Configural",
                                 ifelse(fit_metric == "Failed", "Metric",
                                        ifelse(fit_scalar == "Failed", "Scalar", NA))))

MI_results_temp_2 <- MI_results_temp_1 %>%
  select(Scale, group, MI_test) %>%
  spread(group, MI_test) %>%
  rename(MI_age = age,
         MI_sex = sex) %>%
  mutate(MI_test = ifelse(MI_age == "Passed" & MI_sex == "Passed", "Passed", "Failed")) 

MI_results_temp_3 <- MI_results_temp_1 %>%
  select(Scale, group, MI_test_failed) %>%
  spread(group, MI_test_failed) %>%
  rename(MI_age_test_failed = age,
         MI_sex_test_failed = sex)

MI_results <- full_join(MI_results_temp_2, MI_results_temp_3, by = "Scale") %>%
  select(Scale, MI_test, MI_age, MI_age_test_failed, MI_sex, MI_sex_test_failed)


# save full results to disk for reporting
write_csv(measurement_invariance_full_results, "results/supplementary_results_measurement_invariance_full_results.csv")

```

## Combined table of results

```{r}

combined_results <- cfi_fit_results %>%
  left_join(dist_results,          by = "Scale") %>%
  left_join(consistency_results,   by = "Scale") %>%
  left_join(dependability_results, by = "Scale") %>%
  left_join(stability_results,     by = "Scale") %>%
  left_join(MI_results,            by = "Scale") %>%

  # apply cutoffs to reliability metrics
  dplyr::mutate(alpha_test   = ifelse(alpha >= .7,   "Passed", "Failed"),
                omega_t_test = ifelse(omega_t >= .7, "Passed", "Failed"),
                omega_h_test = ifelse(omega_h >= .7, "Passed", "Failed"),
                dependability_test = ifelse("Test-retest dependability r" >= .7, "Passed", "Failed"),
                stability_test     = ifelse("Test-retest stability r" >= .7,     "Passed", "Failed"),
                test_retest_test = ifelse(dependability_test == "Passed" & stability_test == "Passed", "Passed",
                                          ifelse(dependability_test == "Failed" & stability_test == "Failed", "Failed", NA)),
                overall_scale_test = ifelse(omega_t >= .7 &
                                              ("Test-retest dependability r" >= .7 |
                                                 is.na(`Test-retest dependability r`)) &
                                              ("Test-retest stability r" >= .7 |
                                                 is.na(`Test-retest stability r`)) &
                                              (cfa_test == "Good" | cfa_test == "Mixed") &
                                              MI_test == "Passed", "Good", "Questionable")) %>%
  # reorder columns
  dplyr::select(Scale, n, Items,
                M, SD, Skewness, Kurtosis,
                # internal consistency
                alpha, alpha_ci_lower, alpha_ci_upper, alpha_test, 
                omega_t, omega_t_ci_lower, omega_t_ci_upper, omega_t_test,
                omega_h, omega_h_ci_lower, omega_h_ci_upper, omega_h_test,
                # test-retest reliability
                "Test-retest dependability n", "Test-retest dependability r", 
                "dependability r lower", "dependability r upper", dependability_test,
                "Test-retest stability n", "Test-retest stability r", "stability r lower", "stability r upper", stability_test,
                test_retest_test,
                # cfa fit
                chisq, "chisq/df", df, pvalue,
                cfi, tli, rmsea, rmsea.ci.lower, rmsea.ci.upper, srmr, cfa_test, 
                # measurement invariance
                MI_age, MI_age_test_failed, MI_sex, MI_sex_test_failed, MI_test, 
                # summary
                overall_scale_test,
                # details
                Changes, Interpretation) %>%
  arrange(Scale)

# write to disk
write_csv(combined_results, "results/main_results_table.csv", na = "")

```

## Summary table

```{r}

# convert string conclusions to binary pass/fail
binarized_combined_results <- combined_results %>%
  mutate(alpha_test         = ifelse(alpha_test == "Passed", 1, 
                                     ifelse(alpha_test == "Failed", 0, NA)),
         test_retest_test   = ifelse(test_retest_test == "Passed", 1, 
                                     ifelse(test_retest_test == "Failed", 0, NA)),
         cfa_test           = ifelse(cfa_test == "Mixed" | cfa_test == "Good", 1, 
                                     ifelse(cfa_test == "Poor", 0, NA)),
         MI_test            = ifelse(MI_test == "Passed", 1,
                                     ifelse(MI_test == "Failed", 0, NA)),
         overall_scale_test = ifelse(overall_scale_test == "Good", 1, 
                                     ifelse(overall_scale_test == "Questionable", 0, NA))) %>%
  select(Scale, 
         alpha_test, 
         test_retest_test,
         cfa_test, 
         MI_test, 
         overall_scale_test)

# summarize across scales
summarized_combined_results <- binarized_combined_results %>%
  gather(key, value, -Scale) %>%
  group_by(key) %>%
  summarize(percent = as.character(round(mean(value, na.rm = TRUE)*100, 1))) %>%
  spread(key, percent) %>%
  mutate(Scale = "Summary")

# create table of summarized results
summary_table <- combined_results %>%
  bind_rows(summarized_combined_results) %>%
  rename("Internal consistency" = alpha_test,
         "Test-retest reliability" = test_retest_test, 
         "Confirmatory factor structure" = cfa_test, 
         "Measurement invariance" = MI_test, 
         "Global structural validity" = overall_scale_test) %>%
  select(Scale, 
         "Internal consistency",
         "Test-retest reliability",
         "Confirmatory factor structure",
         "Measurement invariance",
         "Global structural validity")

write_csv(summary_table, "results/main_results_summary.csv", na = "")

summary_table %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

# Alluvial plot

```{r fig.height=4, fig.width=7}

# subset
data_alluvial_plot <- binarized_combined_results %>%
  dplyr::count(alpha_test, test_retest_test, cfa_test, MI_test) %>%
  rownames_to_column() %>%
  tidyr::gather(key = "metric",
                value = "validity",
                -c(rowname, n)) %>%
  mutate(validity = ifelse(is.na(validity), 2, validity),
         validity = dplyr::recode(validity,
                                  `0` = "Fail",
                                  `1` = "Pass",
                                  `2` = "NA"),
         validity = forcats::fct_relevel(as.factor(validity),
                                         "Fail", "NA", "Pass"),
         metric = dplyr::recode(as.character(metric),
                                "alpha_test" = "Internal\nconsistency",
                                "test_retest_test" = "Test-retest\nreliability",
                                "cfa_test" = "Factor\nstructure",
                                "MI_test" = "Measurement\ninvariance"),
         metric = forcats::fct_relevel(as.factor(metric),
                                       "Internal\nconsistency",
                                       "Test-retest\nreliability",
                                       "Factor\nstructure",
                                       "Measurement\ninvariance"))

# alluvial plot with flow
ggplot(data_alluvial_plot,
       aes(x = metric,
           stratum = validity,
           alluvium = rowname,
           y = n,
           fill = validity,
           label = validity)) +
  geom_flow(alpha = .5) +
  geom_stratum(alpha = .8) +
  theme_classic() +
  geom_text(stat = "stratum", size = 3) + # , angle = 90
  theme(legend.position = "none") +
  ylab("Number of scales\nmeeting criteria") +
  xlab("") +
  scale_fill_viridis_d(option = "viridis", direction = -1, begin = 0.3, end = 0.7)

```
